NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-17 ms_nihao_budget.tex
explained why we don't compare our result with the previous cosmological simulations and rephrase the conclusion of Thales' paper

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Several theoretical studies with cosmological simulations
have constrained the phase and cosmological environments of
the potential reservoirs of the missing baryons 
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is a major potential  reservoir
of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to
detect cold gas in the CGM.  Meanwhile, theoretical work has
predicted that a substantial  portion of the CGM is in the warm or
hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
through photoionization, accretion shocks or shocks caused by
galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
10^{4.5-7}$ K, so the detection is dominated by metal lines,
e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  A number of large volume
cosmological simulations \citep{Ford13, Ford15, Suresh15b,
  Oppenheimer16} and zoom-in cosmological simulations
\citep{Stinson12, Hummels13, Shull14} have given predictions for the
\hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
column density profile of \ovi{} and \hi{} in the CGM of galaxies
from the NIHAO \citep{Wang15} cosmological hydrodynamical
simulation suite with observations, studied the covering fraction of
dense \hi{}, looked at the shape of the CGM and its chemical
composition. The conclusion shows the simulations can reproduce the
observation properties well.

>>>>

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates {\bf (mainly about stars and cold gas)} is only 3-8\% of 
the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Several theoretical studies with cosmological simulations
have constrained the phase of
the potential reservoirs of the missing baryons {\bf in intergalactic
medium (IGM), and find a large fraction of the baryons with low density
and high temperature resides between the galaxies}
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is {\bf another}  major potential  reservoir
of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to
detect cold gas in the CGM.  Meanwhile, theoretical work has
predicted that a substantial  portion of the CGM is in the warm or
hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
through photoionization, accretion shocks or shocks caused by
galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
10^{4.5-7}$ K, so the detection is dominated by metal lines,
e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  A number of large volume
cosmological simulations \citep{Ford13, Ford15, Suresh15b,
  Oppenheimer16} and zoom-in cosmological simulations
\citep{Stinson12, Hummels13, Shull14} have given predictions for the
\hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
column density profile of \ovi{} and \hi{} in the CGM of galaxies
from the NIHAO \citep{Wang15} cosmological hydrodynamical
simulation suite with observations, studied the covering fraction of
dense \hi{}, looked at the shape of the CGM and its chemical
composition. The conclusion shows {\bf the simulation can reproduce 
the observational covering fraction and column density profile
of cool \hi{} well, and echo observed \ovi{} column density trend.
As commonly in other simulations, however, the column density of \ovi{}
is lower and the extent of optically thick \hi{} is smaller than
observed.}
